%---------------------------------------------------------------------------%
%->> Frontmatter
%---------------------------------------------------------------------------%
%-
%-> 生成封面
%-
\maketitle% 生成中文封面
\MAKETITLE% 生成英文封面
%-
%-> 作者声明
%-
% \makedeclaration% 生成声明页
%-
%-> 中文摘要
%-
\intobmk\chapter*{摘\quad 要}% 显示在书签但不显示在目录
\setcounter{page}{1}% 开始页码
\pagenumbering{Roman}% 页码符号

自2019年末一种新型冠状病毒（COVID-19）在我国武汉被发现以来，人们的日常生活收到了极大的影响。昔日车水马龙的街道上冷冷清清，再也没有以往的欢声笑语。这样的环境给我们带来了恐慌，因此疫情数据的监测与预测也越来越显得重要。及时、准确的疫情数据对于国家政策的制定、社会的经济发展具有十分重要的意义。

此平台以腾讯疫情数据网站所公布各省市、国内外疫情数据作为研究对象，使用Python爬取数据并将数据存储于MySQL数据库中，然后使用Flask技术将数据可视化展现在面板中以供监测，并提供累计确诊地图、新增确诊病例地图。

\keywords{Python，Flask，COVID-19，数据可视化，MySQL}% 中文关键词
%-
%-> 英文摘要
%-
\intobmk\chapter*{Abstract}% 显示在书签但不显示在目录

Since the end of 2019, a New Coronavirus (COVID-19) was discovered in Wuhan, China, and people's daily life has been greatly affected. The busy streets of the past were deserted, without the laughter of the past. Such an environment has brought us panic, so the monitoring and prediction of epidemic data is becoming more and more important. Timely and accurate epidemic data is of great significance for the formulation of national policies and social and economic development.

This platform takes the epidemic data of provinces and cities, domestic and foreign countries published by Tencent epidemic data website as the research object, uses Python to crawl the data and store the data in MySQL database, then uses flask technology to visualize the data in the panel for monitoring, and provides cumulative confirmed map and new confirmed case map.

\KEYWORDS{Python, Flask, COVID-19, Data Visualization, MySQL}% 英文关键词
%---------------------------------------------------------------------------%